Croder: Bringing the Knowledge of the Crowds into the IDE

### 2013-05-03 paper/paper.tex
Command tweek are removed a useless line
Being a format nazi here
completed part of introduction

\section{Introduction}
\section{Why integrate reviews into the IDE}

>>>>

\section{Introduction}

Crowdsourced computing tasks have been sprouting everywhere lately, spanning over a diverse field of task types. They range from demographic studies (surveys), to personal inquiries (product preferences), to machine learning algorithm training (categorizing photos) and so on and so forth. One is limited only by imagination when customizing tasks for the crowd.

This spike in crowdsourced work has been instigated by the rise of supporting platforms as well. Mechanical Turk\footnote{\url{https://www.mturk.com/mturk/}} has risen to be the \textit{de facto} crowdsourcing platform. The large worker base that this platform has enables a high degree of parallel task decomposition. Moreover, the same large worker base enables rapid task response times. By means of these two crucial characteristics crowdsourcing has become a viable means towards task execution and decomposition.

An interesting application for crowdsourcing is in collaborative design. Workers with or without specialized knowledge participate to create something with a higher scope than the individual task. It falls to the requester's creativity to build tasks in such a way that by composing their results a bigger, holistic product is achieved.

Starting from the previous observation and from related work as well we decided to explore the space of crowdsourced software development tasks. In this regard we cross-referenced the particularities of the crowd with the particularities of software development tasks in order to find suitable candidates. We produced three potential tasks that would be suitable for crowdsourcing: code reviews, test generation and semi-mechanical code transformations.

For the scope of this paper we focused on code reviews for reasons detailed in the

what if progr tasks. integrate with IDE

specialize on code review

tool

benefit from stack exchange

preliminary used study?

\section{Why integrate reviews into the IDE}
